\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsfonts,mathtools}
\usepackage{array,booktabs,enumitem,graphicx,xcolor,hyperref}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\title{Chern-Simons Dynamics and the Quantum Hall Effect}
\author{Source-backed arXiv sample}
\date{}
\begin{document}
\maketitle
\section{Extracted Lists}

The list environments below are extracted from arXiv LaTeX source and wrapped for pdfLaTeX validation.

\begin{enumerate}

\item For reviews of QHE, see, ``The Quantum Hall Effect", edited by
R.E. Prange and S. Girvin (Springer-Verlag, New York, 1987);
G. Morandi, ``Quantum Hall Effect" (Bibliopolis, Napoli, 1988);
A.P. Balachandran, E. Ercolessi, G. Morandi and A.M. Srivastava, `` The
Hubbard Model and Anyon Superconductivity", Int. J. Mod. Phys. B4 (1990) 2057
and Lecture Notes in Physics, Volume 38 (World Scientific, Singapore, 1990);
F. Wilczek, ``Fractional Statistics and Anyon Superconductivity" (World
Scientific, Singapore, 1990) and articles therein. See also ref. 2.

\item T. Chakraborty and P. Pietil\"{a}inen, ``The Fractional
Quantum Hall Effect", (Springer-Verlag, Berlin, 1988).

\item S.C. Jhang, T.H. Hansson and S. Kivelson, Phys. Rev. Lett.
62 (1989) 82; B. Blok and X.G. Wen, Institute for Advanced Study
preprint IASSNS -HEP - 90/23 (1990).

\item J. Fr\"{o}hlich and T. Kerler, Nucl. Phys. B 354 (1991) 369;
J. Fr\"{o}hlich and A. Zee, Institute for Theoretical Physics,
Santa Barbara preprint  NSF-ITP-91-31 (1991).

\item B.I. Halperin, Phys. Rev. B25 (1982) 2185.

\item A.P. Balachandran, G. Bimonte, K.S. Gupta and A. Stern,
Syracuse University preprints SU-4228-477 and 487 (1991).

\item E. Witten, Commun. Math. Phys. 121 (1989) 351.

\item For a review, see P. Goddard and D. Olive, Int. J. Mod. Phys.
A1 (1986) 303.

\item Cf. A.P. Balachandran, G. Marmo, B.-S. Skagerstam and A. Stern,
``Classical Topology and Quantum States" (World Scientific,
Singapore, 1991), Part I.

\item E. Witten, Nucl. Phys. B311 (1988) 46.

\end{enumerate}
\end{document}
