\section{Related Works}
\noindent\textbf{Panorama Representations.} Panoramic images are often projected from spherical space to the 2D plane for processing and storage~\cite{ai2025survey}. 
%
\textbf{Equirectangular Projection (ERP)} is the most popular format, which uniformly maps pixels from a spherical surface to a planar rectangle.
%
Despite its simplicity and spatial continuity, ERP inevitably brings disadvantages such as geometric distortion at the poles.
%
\textbf{Cubemap Projection (CP)}, on the other hand, projects panoramas to six cube faces with the FoV of $90^\circ\times90^\circ$ to alleviate geometric distortion. 
%
However, under this representation, only one cube face is explicitly spatially continuous with its four adjacent faces on the 2D plane.


 
\noindent\textbf{Panorama Generation.} Panoramic image generation~\cite{kalischek2025cubediff,Tang2023mvdiffusion, wu2023panodiffusion, Ye2024DiffPano, feng2023diffusion360, chen2022text2light, liu2024panofree, panfusion2024, wang2023360, shum2023conditional, wang2024customizing, li2023panogen} aims to synthesize 360-degree immersive images based on user-provided textual or visual clues. 
%
It requires the generated images to be seamless in spherical space while maintaining rationality in any perspective anchor. 
%
Recent studies~\cite{kalischek2025cubediff,Tang2023mvdiffusion, wu2023panodiffusion, Ye2024DiffPano, panfusion2024, wang2023360, wang2024customizing, li2023panogen} leverage powerful image diffusion models to generate high-quality panoramic images. 
%
Benefiting from the great generative capabilities of diffusion models, these works have made significant advancements in omnidirectional image synthesis.
%
Among them, PanoGen~\cite{li2023panogen} achieves high-quality results in indoor scenarios by introducing a recursive outpainting and stitching mechanism. 
%
PanFusion~\cite{panfusion2024} proposes a dual-branch pipeline to integrate equirectangular features and perspective features.
%
CubeDiff~\cite{kalischek2025cubediff} uses an alternative representation, cubemap, to synthesize panoramic images with high fidelity and diversity.
%
Despite the significant progress in omnidirectional image generation, achieving similar success in the field of video remains a challenging problem, as it requires spatial-temporal consistency across the entire spherical space, as well as costly computational resources.


A few works~\cite{wang2024360dvd, li20244k4dgen, ma2024vidpanos, tan2024imagine360} explore panoramic video generation. 
%
4K4DGEN~\cite{li20244k4dgen} animates a given high-resolution panoramic image through user intention.
%
However, the requirement of high-quality panoramic inputs limits the application scenarios, as it struggles to generate omnidirectional content without the given images.
%
VidPanos~\cite{ma2024vidpanos} extends a given video to a larger FoV by using Temporal Coarse-to-Fine and Spatial Aggregation strategies,  but it does not produce $360^\circ\times180^\circ$ FoV panoramas.
%
360DVD~\cite{wang2024360dvd} trains a 360-Adapter to exploit the generative capabilities of text-to-video diffusion models, achieving text-driven 360-degree video generation.
%
Most relevant to our work, Imagine360~\cite{tan2024imagine360} utilizes a dual-branch design, similar to~\cite{panfusion2024}, to synthesize panoramic videos from given perspective inputs. 
%
However, the equirectangular videos generated by both 360DVD~\cite{wang2024360dvd} and Imagine360~\cite{tan2024imagine360} exhibit severe distortion, especially at the poles, significantly degrading the sense of immersion and realism.
%
We argue that the spatial distortion and motion drifting caused by ERP make it difficult for models to effectively understand the polar regions with limited training data. 
%
After all, generating perspective videos with extreme motion is still a challenge, let alone panoramas.


\noindent\textbf{Video Outpainting.} Formally, extending from a given perspective view to a panoramic video is a kind of video outpainting task.
%
Benefiting from pretrained diffusion models~\cite{ho2020denoising,song2020denoising,rombach2022high,guo2023animatediff}, previous works~\cite{wang2024your,chen2024follow} have made notable progress in perspective video outpainting. 
%
However, due to the scarcity of 360-degree video data and the modality gap introduced by its unique representation form, panoramic video outpainting remains an open question.
%
In this paper, we design a novel panorama representation format to fully exploit the generative priors of video diffusion models, aiming to address the absence of high-quality panoramic video outpainting.


