\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsfonts,mathtools}
\usepackage{booktabs,multirow,array,tabularx}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algpseudocode}
\title{Algorithm Sample 3}
\author{Dataset-expansion sample}
\date{}
\begin{document}
\maketitle
\section{Procedure}
The pseudocode below is drawn from a source-backed image-to-LaTeX benchmark and reproduced verbatim.

\begin{algorithmic}
[1]
\State Initialize actor network $\mu_\theta$ and critic networks $Q_{\omega_1}$ and $Q_{\omega_2}$.
\State Initialize corresponding target networks: $\theta' \leftarrow \theta$, ${\omega'}_1 \leftarrow \omega_1$, ${\omega'}_2 \leftarrow \omega_2$ and choose $\rho_\text{p} \in (0, 1)$.
\State Initialize replay buffer $\mathcal{R}$.
\State Choose a batch size $K$, a gradient based optimization algorithm and a corresponding learning rate $\lambda_\text{actor}, \lambda_\text{critic} > 0$ for both optimization procedures, a time step size $\Delta t$ and a stopping criterion.
\State Choose standard deviation exploration noise $\sigma_\text{expl}$ and lower and upper action bounds $a_\text{low}, a_\text{high}$.
\Repeat
\State Select clipped action and step the environment dynamics forward.
\begin{equation*}
a= \text{clip}(\mu_\theta(s) + \epsilon, a_\text{low}, a_\text{high}), \quad \epsilon \sim \mathcal{N}(0, \sigma_\text{expl}).
\end{equation*}
\State Observe next state $s'$, reward $r$, and done signal $d$ and store the tuple $(s, a, r, s', d)$ in the replay buffer.
\If{$s'$ is terminal}
\State Reset trajectory.
\EndIf
\For{$j$ in range(\textit{update frequency})}
\State Sample batch $\mathcal{B} = \{(s^{(k)}, a^{(k)}, r^{(k)}, {s'}^{(k)}, d^{(k)})\}_{k=1}^K$ from replay buffer.
\State Compute targets (Clipped Double Q-learning and policy smoothing).
\begin{equation*}
y(r, s', d) = r + (1-d) \min\limits_{i=1, 2} \left\{ Q_{{\omega'}_i}(s', \tilde{a}) \right\}, \quad \tilde{a}= \text{clip}(\mu_{\theta'}(s) + \epsilon, a_\text{low}, a_\text{high}), \quad \epsilon \sim \mathcal{N}(0, \sigma_\text{target}).
\end{equation*}
\State Estimate critic gradient $\nabla_\omega L(Q_\omega^{\mu_\theta})$ by
\begin{equation*}
\nabla_{\omega_i} \Biggl(\frac{1}{K} \sum\limits_{k=1}^K \left(Q_{\omega_i}(s^{(k)}, a^{(k)}) - y(r^{(k)}, {s'}^{(k)}, d^{(k)}) \right)^2 \Biggr), \quad \text{for} \,\, i=1,2.
\end{equation*}
\State Update the critic parameters $\omega_i$ based on the optimization algorithm.
\If{$j \text{ mod } \textit{policy delay frequency} = 0$}
\State Estimate actor gradient $\nabla_\theta J(\mu_\theta)$ by
\begin{equation*}
\nabla_{\theta} \Biggl(\frac{1}{K} \sum\limits_{k=1}^K Q_{\omega_1}(s^{(k)}, \mu_\theta(s^{(k)})) \Biggr).
\end{equation*}
\State Update the actor parameters $\theta$ based on the optimization algorithm.
\State Update target networks softly:
\begin{equation*}
\theta' \leftarrow \rho_\text{p} \theta' + (1 - \rho_\text{p})\theta, \quad
{\omega'}_i \leftarrow \rho_\text{p} {\omega'}_i + (1 - \rho_\text{p})\omega_i, \quad \text{for} \, \, i=1, 2.
\end{equation*}
\EndIf
\EndFor
\Until{stopping criterion is fulfilled.}
\end{algorithmic}

\end{document}
